outline of questions

### 2017-04-25 analysis/first-analysis.Rmd
Files commited by wflow_commit.

This is one of the old quesitons and I think I would like to keep this question.

@@

- We are not sure if this optimazation problem is convex or not.

@@

- To solve this problem might be more computationaly intensive comparing with BCV which just need to calculate svd and general inverse.

@@

#### 2.1  2 by 2 case

Here we take the simpliest example: 2 by 2 matrix $\begin{pmatrix} a & b \\ c & d  \end{pmatrix}$

@@

As I understand here, in the simpliest case, $\begin{pmatrix} a & b \\ c & d  \end{pmatrix}$ is $2 \times 2$ matrix and we assume the this matrix is a rank one matrix. So we can use $a = bd^{-1}c$ to "impute" (or "predict") the value of $a$.

@@

#### 2.1.1 OCV in 2 by 2 case

@@

But what if we solve the together as we discussed previously on Orthogonal Cross Validation (OCV)?

@@

  missing= array(0,dim = c(k_fold,N,P))
  foldindex = array(0,dim = c(k_fold,k_fold,2))
  for(i in 1:k_fold){
    for(j in 1:k_fold){
      foldindex[i,j,1] = i
      foldindex[i,j,2] = (i+j) %% k_fold
    }
  }
  foldindex[which(foldindex == 0)] = k_fold
  for(i in 1:k_fold){
    missing[i, , ] = Y
    for(j in 1:k_fold){
      missing[i,rowindex[,foldindex[j,i,1]],colindex[,foldindex[j,i,2]]] = NA
    }
  }
  par(mfrow = c(2,2), mar = (c(5,4,4,2)-1.9))
  image(Y,main = "data Y")
  for(i in 1:k_fold){
    image(missing[i,,],main = "missing data")
  }
  return(missing)
}

N = 3
P = 3
Y = matrix(rep(1,N*P),ncol =  P)
g = cross_plot(Y)
```

@@

Then the MSE for each row and column permutation would be:

\begin{eqnarray}
MSE &=& MSE_1 + MSE_2 + MSE_3\\
 &=& ||\hat{Y}_{(1)} - Y_{(1)}||_2 + ||\hat{Y}_{(2)} - Y_{(2)}||_2 + ||\hat{Y}_{(3)} - Y_{(3)}||_2
\end{eqnarray}

#### 2.3 2 by 2 matrix again

@@

The question is can we get better idea by solving problem (2.1) and (2.2) together (by taking the average of MSE)?

@@

\begin{eqnarray}
& & \min_{u,v,\lambda} MSE_1 + MSE_2\\
&s.t.& uu^T = I\\
&& v v^T = I \\
&& \lambda >0 \\
&where& MSE_1 = ||a - u_0\lambda v_0||_F + ||d - u_1 \lambda v_1||_F\\
&and& MSE_2 = ||b - u_0\lambda v_1||_F + ||c - u_1 \lambda v_0||_F
\end{eqnarray}

@@

>>>>

__This is one of the old quesitons and I think I would like to keep this question.__

@@

- We are not sure if this optimization problem is convex or not.

@@

- To solve this problem might be more computationally intensive comparing with BCV which just need to calculate svd and general inverse.

@@

#### 2.1 Toy example: 2 by 2 case

Here we take the simplest example: 2 by 2 matrix $\begin{pmatrix} a & b \\ c & d  \end{pmatrix}$

@@

As I understand here, in the simplest case, $\begin{pmatrix} a & b \\ c & d  \end{pmatrix}$ is $2 \times 2$ matrix and we assume the this matrix is a rank one matrix to make the determinant equal to zero. So we can use $a = bd^{-1}c$ to "impute" (or "predict") the value of $a$. __Thus we can get the solution.__

@@

#### 2.1.2 OCV in 2 by 2 case

@@

**But what if we solve them together as we discussed previously using Orthogonal Cross Validation (OCV)?**

@@

  missing= array(0,dim = c(k_fold,N,P))
  foldindex = array(0,dim = c(k_fold,k_fold,2))
  for(i in 1:k_fold){
    for(j in 1:k_fold){
      foldindex[i,j,1] = i
      foldindex[i,j,2] = (i+j) %% k_fold
    }
  }
  foldindex[which(foldindex == 0)] = k_fold
  for(i in 1:k_fold){
    missing[i, , ] = Y
    for(j in 1:k_fold){
      missing[i,rowindex[,foldindex[j,i,1]],colindex[,foldindex[j,i,2]]] = NA
    }
  }
  par(mfrow = c(2,2), mar = (c(5,4,4,2)-1.9))
  image(Y,main = "data Y")
  for(i in 1:k_fold){
    image(missing[i,,],main = "missing data")
  }
  return(missing)
}
set.seed(999)
N = 3
P = 3
Y = matrix(rep(1,N*P),ncol =  P)
g = cross_plot(Y)
```

@@

For each row and column permutation, we calculate the MSE as follows:

\begin{eqnarray}
MSE &=& MSE_1 + MSE_2 + MSE_3\\
 &=& ||\hat{Y}_{(1)} - Y_{(1)}||_F^2 + ||\hat{Y}_{(2)} - Y_{(2)}||_F^2 + ||\hat{Y}_{(3)} - Y_{(3)}||_F^2
\end{eqnarray}

#### 2.3 back to 2 by 2 matrix again

@@

- problem (2.1)

\begin{eqnarray}
& & \min_{u^*, v^*, \lambda^*, b, c} ||b - u_0^*\lambda^* v_1^*||_F^2 + ||c - u_1^* \lambda^* v_0^*||_F^2\\
&s.t.& u^*u^{*T} = I\\
&& v^* v^{*T} = I \\
&& \lambda^* >0 \\
& & ||a - u_0^*\lambda^* v_0^*||_F^2 + ||d - u_1^* \lambda^* v_1^*||_F^2 = 0
\end{eqnarray}

- problem (2.2)

\begin{eqnarray}
& & \min_{u^{**}, v^{**}, \lambda^{**}, a, d} ||a - u_0^{**}\lambda^{**} v_0^{**}||_F^2 + ||d - u_1^{**} \lambda^{**} v_1^{**}||_F^2\\
&s.t.& u^**u^{**T} = I\\
&& v^{**} v^{**T} = I \\
&& \lambda^{**} >0 \\
& & ||b - u_0^{**}\lambda^{**} v_1^{**}||_F^2 + ||c - u_1^{**} \lambda^{**} v_0^{**}||_F^2 = 0
\end{eqnarray}

**The question is can we get better idea by solving problem (2.1) and (2.2) together (by taking the average of MSE)?** It means that we want $u^*,v^*$ and $u^{**},v{**}$ to be same. Similarly as the MSE in OCV, we would like use the average (sum) of those two MSE.

@@

\begin{eqnarray}
& & \min_{u,v,\lambda} MSE_1 + MSE_2\\
&s.t.& uu^T = I\\
&& v v^T = I \\
&& \lambda >0 \\
&where& MSE_1 = ||a - u_0\lambda v_0||_F^2 + ||d - u_1 \lambda v_1||_F^2\\
&and& MSE_2 = ||b - u_0\lambda v_1||_F^2 + ||c - u_1 \lambda v_0||_F^2
\end{eqnarray}

@@

In practice, we might get $u_0^*, v_0^*, u_1^*, v_1^*$ in $MSE_1$ to predict $a,d$ and get $u_0^{**}, v_0^{**}, u_1^{**}, v_1^{**}$ in $MSE_2$ to predict $b,c$.
